\documentclass{letter}
\usepackage{hyperref}
\signature{Deependra Dhakal}
\address{Baseni \\ Bharatpur-11 \\ Chitwan}
\begin{document}

\begin{letter}{Director \\ Unique Seed Company Pvt. Ltd. \\ Dhangadhi
\\ Kailali, Nepal}
\opening{Dear Sir}

I am writing to you to express my interest to work in your company. I have come across your company's hiring plan through a reputed academic and I would like to be considered for the position of Plant Breeder.

% % The \ldots command produces dots in a way that will not upset
% % the typesetting of the document.
% \ldots 

That said, allow me to express that the opportunity to work in the abovementioned position will be a passionate journey to ideal realization of my academic interest. I am a prospective post-graduate in Genetics and Plant Breeding studies. 

While working on a recent research project, which although serves mostly for a academic degree, I have gained substantially as to what an ideal field researcher in Plant Breeding should be. Since the field is ever-expanding in how and what it contributes to globally, letalone in National context, personally, I have come to realize that building upon experiences and having a clear vision is as important in the field of industry oriented Plant Breeding. Afterall, a seed of potentially impactful kind starts off as merely an off-type in a larger context. 

In citing my relevant experiences so far, I have successfully sought for a research problem mostly using exploratory techniques, written a funding proposal, designed an experiment accounting for both variabilities and resource constraints, performed data gathering, and employed various descriptive and inferential statistics for analytical purposes. I have also developed an alert perspective on reproducible research and report presentation, which I believe your company will benefit the most.

I welcome any opportunity to discuss on how I can bring about positive contribution to your company. Thank you for your time and consideration. I look forward to your reply.

\closing{Yours Faithfully,}

\ps
P.S. You can find an updated CV attached herewith the mail and also at\\
\url{http://rookie.rbind.io/}.

\end{letter}
\end{document}
