---
name: Deependra
surname: Dhakal
position: ""
address: "Siranchowk-3 (Harmi), Gorkha"
phone: +977 9845333283
www: rookie.rbind.io
email: "ddhakal.rookie@gmail.com"
twitter: dd_rookie
github: deependrad
# linkedin: ""
date: "`r format(Sys.time(), '%B %Y')`"
# geometry: "margin=1.25cm"
output: 
  vitae::awesomecv:
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

```

\bpicture
\includegraphics[width=5em]{Photo_pp.jpg}
\epicture

# Education

```{r education}
require(tidyverse)
tribble(
  ~ Year, ~ Degree, ~ Institution, ~ Location, ~ Score, ~ Board,
  "2016--2018", "M. Sc. Ag. (Plant Breeding and Genetics)", "Agriculture and Forestry Campus, Rampur", "Chitwan", "First Division", "Agriculture and Forestry University",
"2010--2015", "B. Sc. (Agriculture)", "Institute of Agriculture and Animal Science", "Lamjung", "First Division", "Tribhuvan University",
"2008--2010", "Higher Secondary Level (10+2 in Science)", "Orchid Science College", "Chitwan", "First Division", "Higher Secondary Education Board",
"2008", "School Leaving Certificate", "Small Heaven Higher Secondary Boarding School", "Chitwan", "Distinction", "SLC Board"
) %>% 
  vitae::detailed_entries(what = Institution, when = Year, with = Board, where = Location, why = Score)

```

# Competencies

## Computing

### Scripting {-}

\begin{multicols}{2}
\begin{itemize}
\item Python, 
\item R, 
\item Bash,
\item Javascript,
\item Markdown,
\item \LaTeX,
\item HTML
\end{itemize}
\end{multicols}

### Domain applications {-}

\begin{multicols}{2}
\begin{itemize}
\item Crop modeling
\item DSSAT
\item GIS and spatial analysis
\item QGIS
\end{itemize}
\end{multicols}

### General purpose applications {-}

\begin{multicols}{2}
\begin{itemize}
\item ImageMagick,
\item Tesseract,
\item MS Word, MS Excel, VBscript,
\item Adobe Photoshop
\end{itemize}
\end{multicols}

## Communication Language

- Nepali
- English
- Hindi

# Training and Experience


```{r t-n-e}

experience_training <- tribble(
  ~ Period, ~ Program, ~ Location, ~ Organizer, ~ Position, ~ Affiliation,
  "April 13 2022-- Ongoing", "Agriculture and Forestry University", "Rampur, Chitwan, Nepal", NA, "\\textit{Assistant Professor}", "Department of Genetics and Plant Breeding",
  "April 21 2021-- April 12, 2022", "Ministry of Land Management, Agriculture and Cooperative", "Pokhara, Kaski, Nepal", NA, "\\textit{Crop Development Officer}", "Seed Laboratory, Gandaki Province",
  "March 29 2019--December 2020", "Gokuleshwor Agriculture and Animal Science College", "Baitadi, Nepal", NA, "\\textit{Assistant Professor}", "Department of Plant Breeding and Genetics",
  "May 9, 2018--March 28, 2019", "Unique Seed Company Pvt. Ltd.", "Dhangadhi, Kailali, Nepal", NA, "\\textit{Crop Breeder}", "Crop Breeding and Research Division",
  "February 17, 2019--February 18, 2019", "National training workshop on 'Seed Quality and Productivity Enhancement Technologies in Lentil'", "Nepalgunj, Nepal", "Organized by: CIMMYT and NGLRP/NARC", NA, "representing Unique Seed Company Pvt. Ltd.",
  "February 13, 2019--February 15, 2019", "International training workshop on 'Hybrid Vegetable Seed Production and Marketing'", "Dang, Nepal", "Organized by: HRD/NARC, SEAN, CIMMYT and World Vegetable Center", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "October 1, 2018--October 3, 2018", 'International training on "Hybrid Maize Seed Production and Marketing"', "Kathmandu, Nepal", "Organized by: CIMMYT", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "September 29, 2018--September 30, 2018", 'International training on "Statistical Data Analysis"', "Kathmandu, Nepal", "Organized by: CIMMYT", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "July 17, 2018--August 31, 2018", "International training on 'Hybrid Maize Comprehensive Technologies'", "Chitwan, Nepal", "Organized by: Yuan Longping High-Tech Agriculture Co. Ltd., Changsha, China and NMRP/NARC, Nepal", NA, "representing Unique Seed Company Pvt. Ltd.",
  "November 2016--December 2016", "Enhancing quality standards of raw milk: Validation of Good Manufacturing Practices(GMP) in the supply chain.", "Tanahun, Nepal", NA, "\\textit{Field Research Associate}", "FORWARD Nepal",
  "March 2014--April 2014", "Action Research for Cost Effective Agricultural Extension Services in 10 mid-hill districts of Nepal.", "Rukum, Nepal", NA, "\\textit{Enumerator}", "Nepal Development Research Institute")

experience_training %>% 
  mutate(Program = ifelse(!is.na(Organizer), paste0(Program, "; ", Organizer), Program)) %>% 
  select(-Organizer) %>% 
  vitae::detailed_entries(what = Affiliation,
                          when = Period,
                          with = Program,
                          where = Location,
                          why = Position, 
                          .protect = FALSE)

```

# Research interests

```{r interests}
tribble(
  ~ Idea, ~ Specialization,
  "Mathematical modeling", "Cropping systems simulation and inference on ecological data",
  "Geo-spatial statistics", "Feature identification and visual summary of data",
  "Multivariate analysis", "of genotype and phenotype information",
  "Design and optimization of experiments", "Both for controlled environments and without environmental control; Randomization based design and design search algorithms") %>% 
  vitae::brief_entries(what = glue::glue("Interested in {Idea}"),
                       with = Specialization)

```


# Publications

```{r publications}
library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("publications.bib") %>%
  arrange(desc(author$family), issued)

```


# Advisor and Referee

\bmulticols

\columnbreak

### Dr. Madhav Prasad Pandey {-}
  - Professor
  - Department of Genetics and Plant Breeding
  - Agriculture and Forestry University
  - 9855081410
  - \href{mailto:mppandey@afu.edu.np}{mppandey@afu.edu.np}

### Dr. Krishna Hari Dhakal {-}
  - Chairman
  - Department of Genetics and Plant Breeding
  - Agriculture and Forestry University
  - 9843561486
  - \href{mailto:khdhakal@afu.edu.np}{khdhakal@afu.edu.np}

\columnbreak

### Mr. Laxmi Kant Dhakal {-}
  - Chairman
  - Unique Seed Company Pvt. Ltd.
  - Dhangadhi, Kailali
  - 9858420560
  - \href{mailto:krishak14@gmail.com}{krishak14@gmail.com}

\emulticols

\vspace{1.5cm}
\parbox[t]{\textwidth}{
{\bfseries Declaration}\par

I hereby declare that, all the information stated above is true and genuine in my belief. I can dispense any and/or all of the mentioned works in verified form whenever demanded.
}
