---
name: Deependra
surname: Dhakal
position: ""
address: "Siranchowk-3 (Harmi), Gorkha"
phone: +977 9845333283
www: rookie.rbind.io
email: "ddhakal.rookie@gmail.com"
twitter: dd_rookie
github: deependrad
# linkedin: ""
date: "`r format(Sys.time(), '%B %Y')`"
# geometry: "margin=1.25cm"
output: 
  vitae::awesomecv:
    keep_tex: yes
    includes:
      in_header: preamble.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)

```

\bpicture
\includegraphics[width=5em]{Photo_pp.jpg}
\epicture

# Education

```{r education}
require(tidyverse)
tribble(
  ~ Year, ~ Degree, ~ Institution, ~ Location, ~ Score, ~ Board,
  "2016--2018", "MS (Plant Breeding and Genetics)", "Agriculture and Forestry Campus, Rampur", "Chitwan", "First Division", "(MS; Plant Breeding and Genetics) Agriculture and Forestry University",
"2010--2015", "BS (Agriculture)", "Institute of Agriculture and Animal Science", "Lamjung", "First Division", "(BS; Agriculture) Tribhuvan University",
"2008--2010", "Higher Secondary Level (10+2 in Science)", "Orchid Science College", "Chitwan", "First Division", "Higher Secondary Education Board",
"2008", "School Leaving Certificate", "Small Heaven Higher Secondary Boarding School", "Chitwan", "Distinction", "SLC Board"
) %>% 
  vitae::detailed_entries(what = Institution, when = Year, with = Board, where = Location, why = Score)

```

# Competencies

## Scripting and domain interests {-}

\begin{multicols}{2}
\begin{itemize}
\item R -- Graphical/functional programming and algorithmic development
\item \LaTeX -- TikZ, literate programming
\item Bash -- General purpose scripting, file management, code version control and execution
\item Julia -- Dynamic programming and optimal experimental designing
\item ImageJ and Python  -- Image and algorithmic analysis
\item DSSAT/aquacrop -- Crop physiology studies and environment management decision
\item QGIS and GeoDa -- Geographical data exploration/aggregation
\end{itemize}
\end{multicols}

# Training and Experience


```{r t-n-e}

experience_training <- tribble(
  ~ Period, ~ Program, ~ Location, ~ Organizer, ~ Position, ~ Affiliation,
  "April 13 2022-- Ongoing", "Agriculture and Forestry University", "Rampur, Chitwan, Nepal", NA, "\\textit{Assistant Professor}", "Department of Genetics and Plant Breeding",
  "April 21 2021-- April 12, 2022", "Ministry of Land Management, Agriculture and Cooperative", "Pokhara, Kaski, Nepal", NA, "\\textit{Crop Development Officer}", "Seed Laboratory, Gandaki Province",
  "March 29 2019--December 2020", "Gokuleshwor Agriculture and Animal Science College", "Baitadi, Nepal", NA, "\\textit{Assistant Professor}", "Department of Plant Breeding and Genetics",
  "May 9, 2018--March 28, 2019", "Unique Seed Company Pvt. Ltd.", "Dhangadhi, Kailali, Nepal", NA, "\\textit{Crop Breeder}", "Crop Breeding and Research Division",
  "February 17, 2019--February 18, 2019", "National training workshop on 'Seed Quality and Productivity Enhancement Technologies in Lentil'", "Nepalgunj, Nepal", "Organized by: CIMMYT and NGLRP/NARC", NA, "representing Unique Seed Company Pvt. Ltd.",
  "February 13, 2019--February 15, 2019", "International training workshop on 'Hybrid Vegetable Seed Production and Marketing'", "Dang, Nepal", "Organized by: HRD/NARC, SEAN, CIMMYT and World Vegetable Center", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "October 1, 2018--October 3, 2018", 'International training on "Hybrid Maize Seed Production and Marketing"', "Kathmandu, Nepal", "Organized by: CIMMYT", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "September 29, 2018--September 30, 2018", 'International training on "Statistical Data Analysis"', "Kathmandu, Nepal", "Organized by: CIMMYT", NA, "representing Unique Seed Company Pvt. Ltd.", 
  "July 17, 2018--August 31, 2018", "International training on 'Hybrid Maize Comprehensive Technologies'", "Chitwan, Nepal", "Organized by: Yuan Longping High-Tech Agriculture Co. Ltd., Changsha, China and NMRP/NARC, Nepal", NA, "representing Unique Seed Company Pvt. Ltd.",
  "November 2016--December 2016", "Enhancing quality standards of raw milk: Validation of Good Manufacturing Practices(GMP) in the supply chain.", "Tanahun, Nepal", NA, "\\textit{Field Research Associate}", "FORWARD Nepal",
  "March 2014--April 2014", "Action Research for Cost Effective Agricultural Extension Services in 10 mid-hill districts of Nepal.", "Rukum, Nepal", NA, "\\textit{Enumerator}", "Nepal Development Research Institute")

experience_training %>% 
  mutate(Program = ifelse(!is.na(Organizer), paste0(Program, "; ", Organizer), Program)) %>% 
  select(-Organizer) %>% 
  vitae::detailed_entries(what = Affiliation,
                          when = Period,
                          with = Program,
                          where = Location,
                          why = Position, 
                          .protect = FALSE)

```

# Hobbies and personal projects

```{r interests, results='asis'}
interests <- tribble(
  ~ Idea, ~ Specialization,
  "Mathematical graphics", "Coded flag (The Most Mathematical Flag - Numberphile\\footnote{\\url{https://www.youtube.com/watch?v=f2Gne3UHKHs}}) of Nepal using TikZ; Repository: \\url{https://github.com/DeependraD/flag-of-nepal}.",
  "Study of non-linear systems (crop growth and economy of agricultural products) using dynamic programming", "Distributed lag based enterprise appraisal parametrizing biological fruit growth in Coffee (\\url{https://github.com/DeependraD/distributed-lag-enterprise-simulation}); Price transmission study in Wheat (\\url{https://github.com/DeependraD/macroeconomics_thesis})",
  "Blogging and web", "Maintain a personal website in open-source community hosted domain using Hugo (\\url{https://github.com/DeependraD/dblog})",
  "Colorimetry and image analysis", "Created an adaptation of Munsell Color system for visual rating of leaf color (\\url{https://github.com/DeependraD/munsell_crop_adaptation})")

# interests %>% 
#   vitae::brief_entries(what = Idea,
#                        with = Specialization)

store_text <- knitr::kable(interests, booktabs = TRUE, escape = FALSE, format = "latex") %>% 
  kableExtra::kable_styling(font_size = 9, position = "left") %>% 
  kableExtra::column_spec(column = 1:2, width = c("12em", "40em"))

cat(str_remove(store_text, "\\\\\\\\\\n\\\\bottomrule"))

```


# Publications

```{r publications}
library(dplyr)
# knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("publications.bib") %>%
  arrange(desc(issued))

```


# Advisor and Referee

\bmulticols

\columnbreak

### Madhav Prasad Pandey, PhD {-}
  - Professor
  - Department of Genetics and Plant Breeding
  - Agriculture and Forestry University
  - +977-9855081410
  - \href{mailto:mppandey@afu.edu.np}{mppandey@afu.edu.np}

### Lal Prasad Amgain, PhD {-}
  - Professor
  - Department of Agronomy
  - Tribhuwan University
  - +977-9851219516
  - \href{mailto:amgainlp@gmail.com}{amgainlp@gmail.com}

\columnbreak

### Mahendra Tripathi, PhD {-}
  - Scientist
  - Agronomy/Plant Breeding and Genetics
  - National Maize Research Program (NMRP), Rampur, Nepal
  - +977-9846871041
  - \href{mailto:mptripathi@gmail.com}{mptripathi@gmail.com}

\emulticols

\vspace{1.5cm}
\parbox[t]{\textwidth}{
{\bfseries Declaration}\par

I hereby declare that, all the information stated above is true and genuine in my belief. I can dispense any and/or all of the mentioned works in verified form whenever demanded.
}
