---
output: 
  bookdown::pdf_document2:
    keep_tex: yes
header-includes:
   - \usepackage{longtable}
   - \usepackage{graphicx,subcaption}
   - \usepackage{tabularx}
   - \newcommand{\subfloat}[2][need a sub-caption]{\subcaptionbox{#1}{#2}}
---  

```{r fig-sub, fig.cap='two plots', fig.subcap=c('one plot this one subcaption is supposed to be really really really very long', 'the other one', 'the third one this one caption is not long enought to be wrapped around, I guess. But I could be wrong.', 'the fourth and the obstructive one', 'the fifth and sadistic one', 'the last but not the least one'), out.width='.49\\linewidth', fig.asp=1, fig.ncol = 2}
plot(1:10)
plot(1:10, 3:12)
plot(rnorm(10), pch=19)
plot(rnorm(10), pch=21)
plot(rnorm(10), pch=12)
plot(rnorm(10), pch=14)
```

\small{
\begin{longtable}[]{@{}ll@{}}
\caption{\label{tab:site-fact-tab}Site of study factsheet}\\
\toprule
\textbf{Particulars} & \textbf{Detail}\tabularnewline
\midrule
\endhead
Institution & Agriculture and Forestry University\tabularnewline
Farm & Rampur\tabularnewline
State & Chitwan\tabularnewline
Longitude & \(84.4^o\)\tabularnewline
Latitude & \(27.62^o\)\tabularnewline
Altitude & 191 meters\tabularnewline
Environment & ME1\tabularnewline
Dominant Soil(FAO classification) & Cambisols (Dystric
Cambisols)\tabularnewline
Surface pH & 5\tabularnewline
Cropping system & Rice-wheat\tabularnewline
\bottomrule
\end{longtable}
}


```{r change-dep-var-labs, results='asis', echo=FALSE}
carslin_mod <- lm(mpg ~ hp + cyl + disp + qsec, data = mtcars)
stargazer::stargazer(carslin_mod, 
                     type = "latex", 
               title = "Model summary of mpg approximated by other variables", 
               style = "all", digits = 2, header = FALSE, font.size = "small", 
               column.labels = c("mpg"), 
               model.names = TRUE, dep.var.labels.include = FALSE, 
               report = "vc*sp", covariate.labels = c(letters[1:4]),
               keep = c("hp", "cyl", "qsec"),
               # coef = response_replace_coef[c(1, 2, 3)],
               single.row = TRUE, df = FALSE, omit.stat = c("adj.rsq"),
               column.sep.width = "1pt", float = FALSE)
```


```{r change-dep-var-labs2, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
require(tidyverse)
mtcars1 <- mtcars
mtcars1[,c("cyl", "vs", "am")] <- purrr::map_df(mtcars[,c("cyl", "vs", "am")], as.factor)

carsmix_mod <- lme4::lmer(mpg ~ hp + (1 | cyl) + disp + qsec, data = mtcars1)
carsmix_mod2 <- lme4::lmer(mpg ~ hp + (1 | cyl) + (1 | vs) + disp + qsec, data = mtcars1)
carsmix_mod3 <- lme4::lmer(mpg ~ hp + (1 | am) + disp + vs + cyl, data = mtcars1)

anova(carsmix_mod, 
      carsmix_mod2, carsmix_mod3) %>% 
  broom::tidy() %>% 
  mutate(term = c("Blocking factors", 
                  "Blocking factors + Entry genotypes", 
                  "Blocking factors + Check and entry genotypes")) %>% 
  knitr::kable(format = "latex", 
               booktabs = TRUE, align = "l") %>% 
  kableExtra::kable_styling(latex_options = "HOLD_position") %>% 
  kableExtra::column_spec(1, width = "2.5cm")
  
```

