---
title: "Long table mixing with portrait and landscape"
output:
    bookdown::pdf_document2:
        keep_tex: yes
        includes:
            in_header: long_table_mixing_with_header.tex 
---

```{r setup, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(tidy = TRUE, cache = TRUE, 
                      echo = FALSE, 
                      tidy.opts = list(width.cutoff=50), 
                      eval = TRUE)
options(knitr.kable.NA = "", digits = 3)
suppressPackageStartupMessages(require(tidyverse))
```

# Page display modes and table formatting hacks

## Page display modes: portrait and landscape

- to get every pages in landscape mode, add: `classoption: landscape` to the yaml header.
- `\blandscape` and `\elandscape` commands come from modifications of command in pdflscape package.
- use \LaTeX\ `pdflscape` package instead of `lscape` package to get automatically rotated view of landscape pages in pdf viewer.

Portrait page

\begingroup
\centering
```{r}
summary(cars)
```
\endgroup

\newpage
\blandscape

Landscape page

```{r}
summary(cars)
```

\elandscape

\newpage

## `xtable`: default and sidewaystable environments

- using sidewaystable environment requires `rotating` package to be used in latex preamble.

Portrait table using `xtable` without sidewaystable environment is shown in Table \@ref(tab:xtab-without-sideways).

```{r xtab-without-sideways, results='asis', echo=FALSE}
print(xtable::xtable(summary(cars), caption="Portrait\\label{tab:xtab-without-sideways} table"), comment=FALSE)
```

Landscape table using `xtable` with sidewaystable environment is shown in Table \@ref(tab:xtab-with-sideways).

```{r xtab-with-sideways, results='asis', echo=FALSE}
print(xtable::xtable(summary(cars), caption="Landscape\\label{tab:xtab-with-sideways} table"),
      floating.environment="sidewaystable", comment=FALSE)
```


## `xtable` workaround for landscape and portrait tables in same page

Portrait table is shown in \@ref(tab:same-page-portrait).

```{r same-page-portrait, results='asis', echo=FALSE}
print(xtable::xtable(summary(cars), caption="Portrait\\label{tab:same-page-portrait} table"), comment=FALSE)
```

Landscape table is shown in \@ref(tab:same-page-landscape).

```{r same-page-landscape, results='asis', echo=FALSE}
cat(paste0(
    "\\begin{table}[ht]\n\\centering\\rotatebox{90}{\n",
    paste0(capture.output(
      print(xtable::xtable(summary(cars)), floating=FALSE, comment=FALSE)),
      collapse="\n"),
    "} \n\\caption{Landscape\\label{tab:same-page-landscape} table}", "\n\\end{table}", collapse = "\n"))
```


## Long table with footnotes using `knitr::kable()`

Long table formatted with footnote marks in the table using `knitr::kable()` is shown in Table \@ref(tab:check-vars-info1).

```{r check-vars-info1, results='asis', warning=FALSE, message=FALSE}
checks_data <- read_csv("./data/check-varieties-wheatatlas-info.csv", 
                          na = c("Unknown", "No Info", "")) # chunk option message=FALSE
knitr::kable(x = suppressWarnings(colnames(checks_data) %>% rbind(checks_data) %>% 
               column_to_rownames(var = "Name") %>% 
               t() %>% 
               as.tibble() %>% 
               rename("Characteristics" = "Name")), 
             format = "latex", align = "c", 
             booktabs = TRUE, 
             escape = F,
             longtable = TRUE,
             caption = "A summary of check varieties used in the study") %>% 
  kableExtra::kable_styling(latex_options = "striped", full_width = FALSE) %>% 
  kableExtra::column_spec(1, width = "2.0cm") %>% 
  kableExtra::column_spec(2:5, width = "3.4cm")
```


## Long table with footnotes using panodoc (default) syntax

Four check varieties (Described in Table \@ref(tab:check-vars-info2)), released at different periods, adapted to a range of environmental conditions in Nepal were included alongside in the study.

|    |Aditya^[http://wheatatlas.org/varieties/detail/22373]|Bhrikuti^[http://wheatatlas.org/varieties/detail/22378]|Gautam^[http://wheatatlas.org/varieties/detail/22383]|Tilottama^[http://wheatatlas.org/varieties/detail/26413]|
|:--:|:----:|:------:|:----:|:-------:|
|Year released|2010|1994\*|2002|2014|
|Synonym|HD-2781\*|NL-623\*|BL-1887; NC-1838-4B-020B-020B-2B-0B\*|NL 1073; NL1073; NL-1073; FRANCOLIN; FRANKOLIN|
|Wheat type|Bread|Bread|Bread|Bread|
|Semidwarf (Rht gene)|No Info|Yes|Yes|Yes|
|Grain color|White grain|Unknown|Unknown|Unknown|
|Grain hardiness|Unknown|Unknown|Unknown|Unknown|
|Pedigree|GS348/NL746//NL748; BOBWHITE/C-306/C-591/HW-2004\*|CONTESTADO/COCORAQUE F 75/3/POLLO//FURY/ANAHUAC F 75; CLEMENT/COCORAQUE-75/3/POLLO//FURY/ANAHUAC-75\*|SIDDHARTHA/NG 8319//NL 297 or SIDHHARTHA/NG 8319//NL 297|WAXWING*2/VIVITSI|
|Selection history|HD-2781\*|NL 623 FR 2308-2F-1F-0F; NL-623\*|NC 1838-4B-020B-020B-2B-0B|CGSS-01-B-00056T-099Y-099M-099M-099Y-099M-14Y-0B\*|
|Breeding program|Nepal Agriculture Research Council(NARC)|NARC|NARC|NARC|
|CID (Cross ID)||251774|||
|Accession number||K-63729\*|||
|SID (Selection ID)||0|||
|Origin|Cross made in the country, no CIMMYT parents|Advanced line from CIMMYT|Cross made in the country, one CIMMYT parent|Advanced line from CIMMYT|
|CIMMYT breeding line||||FRANCOLIN|
|Genes|Sr2\*; no-Lr34\*; Glu-A1b\*,Glu-B1i\*,Glu-D1a\*|Lr34\*; Glu-A1b\*,Glu-B1i\*,Glu-D1a\*||Sr2+|
|Suitable megaenvironments|ME1|ME1, ME5|ME1, ME5||
|Notes|Terai, Tars and Lower Valleys up to 500 500 masl; maturity 118 days, yield potential 4.8 t/ha||Irrigated, both normal and late sown condition of whole Terai, Taar and foot-hills (<500 m); maturity 105-115; potential yield - 5t/ha |Resistant to spot blotch. High tillering. Early maturing, stay green, excellent for bread and chapati.|
|Resistance to Ug99 rust|No|No|No|Yes(including to Stem, Yellow and Leaf)|
|Approximate acerage variety grown|38,263(2011-12)|153,055(2011-12)|||

Table: (\#tab:check-vars-info2) A summary of check varieties used in the study
